Universal Anonymous Signatures

### 2022-08-17 prism-backend/research/gsac/introduction-paper.tex
Finishing pass.

\todo{Mention Camenisch, Krenn and Lehmann's work.}

@@

%% Main drawbacks of precedents
\paragraph{Limitations of GS and AC.} %
However, even the generalisation efforts that have independently taken place in
GS and AC, are quickly seen to have limited applicability in the real world. On
the GS side, even though MPS achieves a powerful balance on when a signature is
deanonymizable and what information can be extracted from it, upon closer look,
this information is somehow meaningless. Namely, the notion of identity is not
well defined and, thus, it is not possible to claim whether the value output by
their generalised open function makes sense or even if it is legitimate. Also,
just being able to prove membership at signing time is typically not enough, and
one needs to prove more general claims. That is precisely what AC schemes do,
while also providing a well defined notion of identity via credential
attributes. Precisely, it is this defined concept of identity what enables AC
schemes to state when some information revealed at authentication time is a
forgery or not. On the other hand, the notion of accountability  is barely
present in AC schemes. For instance, non-frameability is not even considered
-- and it is non-frameability what ensures when a user cannot be held
accountable.
%
In any case, perhaps the most impractical limitation of all is that too many
models exist in both fields. Although similar, each model focuses on slightly
different utility variants, making them hardly comparable. And, of course, AC
focus on utility at authentication (signing) time, while GS focus on
utility after signing (authentication) time. To the best of our knowledge, no
model exists that combines both, in a general enough manner. In practice, this
forces system designers to decide which one they do not want to lose -- or,
which one they will lose.

>>>>

@@

%% Main drawbacks of precedents
\paragraph{Limitations of GS and AC.} %
However, even the generalisation efforts that have independently taken place in
GS and AC, are quickly seen to have limited applicability in the real world. On
the GS side, even though MPS achieves a powerful balance on when a signature is
deanonymizable and what information can be extracted from it, upon closer look,
this information is somehow meaningless. Namely, the notion of identity is not
well defined and, thus, it is not possible to claim whether the value output by
their generalised open function makes sense or even if it is legitimate. Also,
just being able to prove membership at signing time is typically not enough, and
one needs to prove more general claims. That is precisely what AC schemes do,
while also providing a well defined notion of identity via credential
attributes. Precisely, it is this defined concept of identity what enables AC
schemes to state when some information revealed at authentication time is a
forgery or not. On the other hand, the notion of accountability  is barely
present in AC schemes. For instance, non-frameability is not even considered
-- and it is non-frameability what ensures when a user cannot be held
accountable.
%
In any case, perhaps the most impractical limitation of all is that too many
models exist in both fields. Although similar, each model focuses on slightly
different utility variants, making them hardly comparable. And, of course, AC
focus on utility at authentication (signing) time, while GS focus on
utility after signing (authentication) time. To the best of our knowledge, no
model exists that combines both, in a general enough manner. Probably, the
closest work to ours, in regard to this ``generalization spirit'', is
\cite{ckl+15}, although it focuses only on anonymous credentials. In practice,
needing to resort to too specific models forces system designers to decide which
feature (utility at or after signing time, etc) they do not want to lose -- or,
which one they will lose.
